Project-I by Group Sao Paulo

### 2015-11-02 report/paper.tex
Update report and PCA

\section{Data Description}
Our train-data consists of ...

\section{Data visualization and cleaning}
We performed basic exploratory data analysis on our data. Figure \ref{fig:boxplotX} ...

\begin{figure}[!h] % !t
\center
\subfigure[Boxplot of real-valued $\mathbf{X}$. Data is not centered and therefore we normalize it.]{\includegraphics[width=2.5in]{figures/boxplotX.pdf} \label{fig:boxplotX}}
\hfill
\subfigure[Histogram of $\mathbf{y}$. We can clearly see two outliers.]{\includegraphics[width=2.5in]{figures/histY.pdf} \label{fig:histY}}
\caption{}
\end{figure}

\section{Ridge regression}
We applied least-squares and ridge regression to this dataset...

\section{Feature transformations}
We tried several feature transformations...

>>>>

\section{Regression}
\subsection{Data Description}
Our regression-data contains $N=2800$ train-examples and $N=1200$ test-data. The train-data are composed of input and output variables $X$ and $y$. Each input $x_n$ has a dimensionality $D=70$ with 60 real-valued variables, 1 binary variable, 5 and 4 categorical variables with respectively 3 and 4 categories. The output of our test-data is not observed. Our goal is then to predict $y$ for all test-examples and to give an approximation of the test-error.

\subsection{Data Visualization and Cleaning}
To visualise our data, we plot histograms to see the distribution of $y$ and of each dimension of X. The input data is not centred, so that we need to normalise it.

Figure \todo{ADD FIGURE} shows the histogram of the output variable. We see that the data are split in three bursts of different sizes : a large amount of the data have small output values and only a small part have the highest values. Figure \todo{ADD FIGURE} shows histograms of two interesting dimensions of $X$. As all others real-valued variables seem to have sort of Gaussian distributions, we can see that those are split in two bursts. By plotting $y$ in function of each of these variables, as shown in Figure \todo{ADD FIGURE}, we can see that $y$ is highly correlated with dimensions $6$ and $55$ of $X$. The output-data can thus be separated in three clusters by looking at $x_n(6)$ ans $x_n(55)$ for each data.

We also computed the eigenvalues of the matrix $X^T X$. As ten eigenvalues are smaller than $10^{-10}$, we will need to transform $X$ to remove those small eigenvalues or to use methods such as ridge regression to lift them.

%\begin{figure}[!h] % !t
%\center
%\subfigure[Boxplot of real-valued $\mathbf{X}$. Data is not centered and therefore we normalize it.]{\includegraphics[width=2.5in]{figures/boxplotX.pdf} \label{fig:boxplotX}}
%\hfill
%\subfigure[Histogram of $\mathbf{y}$. We can clearly see two outliers.]{\includegraphics[width=2.5in]{figures/histY.pdf} \label{fig:histY}}
%\caption{}
%\end{figure}

\subsection{Clustering and Feature Transformations}

\subsection{Methods}
We applied least-squares and ridge regression to this dataset...

\subsection{Feature transformations}
We tried several feature transformations...

\section{Classification}
\subsection{Data Description}
\subsection{Data Visualization and Cleaning}
\subsection{Logistic Regression}
